### 2022-06-02 chapters/fairness/fif/experiments.tex
minor edits

%\clearpage
\section{Empirical Performance Analysis}\label{sec:experiments}
In this section, we perform an empirical evaluation of {\fairXplainer}. In the following, we discuss the experimental setup, the objectives of experiments, and experimental results. { We adjoin the source code and additional experimental results on the effects of maximum order $\lambda$, runtime, accuracy on different datasets and corresponding explanations (Appendix~\ref{sec:additional_experiments}) to the supplementary material.}

>>>>

%\clearpage
\section{Empirical Performance Analysis}\label{sec:experiments}
In this section, we perform an empirical evaluation of {\fairXplainer}. In the following, we discuss the experimental setup, the objectives of experiments, and experimental results. { We adjoin the source code and additional experimental results on the effects of maximum order $\lambda$, runtime, accuracy on different datasets and corresponding explanations (\red{Appendix(ref{sec:additionalexperiments})}) to the supplementary material.}
